The influence of resource use on yield versus sale price trade-off in Australian vineyards

### 2024-03-10 Cover Letter/main.tex
backing up article edits

\hfill
\begin{tabular}{l @{}}
	$29^{th}$ October, 2023\\ % Date
	\textbf{Bryce Ronald William Polley $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Polley (corresponding author) on behalf of all coauthors: Kate Helmsted, Mardi Longbottom, Madeline Mitchell, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}

>>>>

\hfill
\begin{tabular}{l @{}}
	$26^{th}$ January, 2023\\ % Date
	\textbf{Bryce Ronald William Boyd $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Boyd (corresponding author) on behalf of all coauthors: Kate Helmstedt, Mardi Longbottom, Madeline Mitchell, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}
